---
title: "R Notebook"
output: html_notebook
---
 

```{r}
data <- read.csv('../Downloads/Student Content/DATA/gapminder.csv')
head(data)
```

#Exercise 1: Filtering rows based on conditions
## Create a new variable called small_countries that contains records for countries with population less than 1 000 000.
### HINT: you should get 3830 records.


```{r}
# filtering new cols
small_countries <- subset(data, data$population < 1000000)
head(small_countries)
```

# Exercise 2: Filtering rows based on conditions and sorting
## List the countries for which gdp_per_capita in 2011 was over 60000, sorted by gdp_per_capita.
### HINT: you should get 6 records.


```{r}
gdp_per_capita_filter <- subset(data, year == 2011 & gdp_per_capita > 60000)
gdp_per_capita_filter <- gdp_per_capita_filter[order(gdp_per_capita_filter$gdp_per_capita), ]
head(gdp_per_capita_filter)
```


#Exercise 3: Filtering rows based on conditions and identifying distinct values
## 1. Create a variable called europe_82 which contains all the data for Europe where life expectancy is over 82.
## 2. List all the countries that can be found in this subset (there should be 7).
## 3. Provide the code to check your result


```{r}
europe_82 <- subset(data, region == 'Europe' & data$life_expectancy >= 82)
head(europe_82)

```

#Exercise 4: Filtering rows based on conditions, filtering columns, and identifying distinct values
## 1. Create a variable asia_82 that contains the following fields: year, country, gdp_per_capita, life_expectancy for all the countries in Asia region where life expectancy is over 82 that refer to years 2014 and later.
## 2. List all the countries that can be found in this subset (there should be 3).

```{r}
asia_82 <- subset(data, region == 'Asia' & life_expectancy >= 82 & year >= 2014 & gdp_per_capita)
print(asia_82)
```


```{r}
#Corrected
asia_82 <- subset(data, region == "Asia" & life_expectancy > 82 & year >= 2014,
                  select = c(year, country, gdp_per_capita, life_expectancy))
print(asia_82)

```

```{r}
unique_countries <- unique(asia_82$country)
print(unique_countries)

```

